Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-06-01 figures.Rmd
change logistic regression model to THC, THC alpha, and hematocrit

  dplyr::rename(" " = "variable",
                "Healthy volunteers (HV)" = "HV",
                "Uncomplicated malaria (UM) patients" = "UM",
                "Cerebral malaria (CM) patients" = "CM")

  # remove lactate data for HV
  df_clinical_res[11,]$`Healthy volunteers (HV)` <- "--"

@@

```
**Table 1.** A summary of subject information and hematological data. Group patient data presented as median (quartile 1, quartile 3). Note: Sex not recorded for 3 CM patients; Lactate data removed for HV due to inconsistent data.

@@

### Figure 3: Logistic regression on CM vs UM

#### A. PCA

```{r fig3a}
# remove healthy volunteers, Oxy Hb, and Deoxy Hb from analysis
df_hbox_log_voi <- df_hbox_voi %>% 
  dplyr::filter(Status != "HV") %>% 
  dplyr::select(-(2:5))

@@

# convert to 0s and 1s
df_hbox_voi_01 <- df_hbox_log_voi %>% mutate(Status = ifelse(Status == "CM", 1, 0) %>% as.factor())

# select only significant variables
df_hbox_model <- df_hbox_voi_01 %>% 
  dplyr::select(c(Status, THCα)) %>% 
  mutate(`1/10 * THCα` = THCα/10) %>% 
  dplyr::select(-THCα)

# resample
set.seed(123)
hbox_boot <- bootstraps(df_hbox_model, times = 1000)

@@

# save objects so model doesn't rerun 
save(glm_res, hbox_final, file = "glm_model.Rdata")

@@

**Figure 3** Logistic regression model discriminating CM vs UM patients using only THCα as the predictor. **(A)** PCA of patients with CM and UM as determined by NIRS variables. Color indicates patient status, ellipses show median and 95% confidence interval on the cluster. **(B)** Confusion matrix representing the results of the logistic regression model averaged across 1000 bootstrap resamples. Percent occurrence indicates percentage times that the event (shown by the x- and y-axes) occurred.

>>>>

  dplyr::rename(" " = "variable",
                "Healthy volunteers" = "HV",
                "Uncomplicated malaria patients" = "UM",
                "Cerebral malaria patients" = "CM")

  # remove lactate data for HV
  df_clinical_res[11,]$`Healthy volunteers` <- "--"

@@

```
**Table 1.** A summary of subject information and hematological data. Group patient data presented as median (quartile 1, quartile 3). Note: Sex not recorded for 3 CM patients; Lactate data removed for healthy volunteers due to inconsistent data.

@@

### Figure 3: Logistic regression model on CM vs UM

#### A. PCA
```{r fig3a}
# include variables of interest (THC, THC alpha, and hematocrit), remove healthy volunteers from analysis
df_hbox_log_voi <- df_hbox_impute %>% 
  dplyr::select(c(2,4:5,19:22)) %>% 
  dplyr::filter(Status != "HV")

@@

# select THC, THC alpha, and hematocrit
  df_hbox_model <- df_hbox_impute %>% 
    dplyr::select(c(2,4:5,19:22)) %>% 
    mutate(`1/10 * THCα` = THCα/10, `1/10 * THC` = THC/10) %>% 
    dplyr::select(-c(THCα, THC)) %>% 
    mutate(Status = as.factor(ifelse(Status == "CM", 1, 0))) %>%

    dplyr::select(-c(`Cerebral O2 sat`, `Cerebral O2 sat α`, `Lactate (mmol/L)`))

# resample
set.seed(234)
hbox_boot <- bootstraps(df_hbox_model, times = 1000)

@@

# save objects so model doesn't rerun every time we knit
save(glm_res, hbox_final, file = "glm_model.Rdata")

@@

**Figure 3.** Logistic regression model discriminating CM vs UM patients using THC, THCα, and hematocrit as the regressors **(A)** PCA of patients with CM and UM as determined by NIRS variables. Color indicates patient status, ellipses show median and 95% confidence interval on the cluster. **(B)** Confusion matrix representing the results of the logistic regression model averaged across 1000 bootstrap resamples. Percent occurrence indicates percentage times that the event (shown by the x- and y-axes) occurred.
